Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-02-26 analysis/paper/paper.Rmd
This fixes the caption...
Minor edits to paper

    -   2 - Uses proprietary software that most individuals can afford (*e.g.*, Excel, Matlab? (\$500))

@@

    -   1 - Uses expensive proprietary software that only institutions would typically purchase (*i.e.*, ArcGIS standard is \$7000US)

@@

The fourth level includes packaging the analysis as a software package, *e.g.* R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al. [@Khaliq2020] have done.
Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of chickpea ascochyta conida dispersal using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a].

[@Miorini2018, @Miorini2019]

-   Example from Grünwald lab:

    -   paper <http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI>
    -   github repo <https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests>

## A general workflow

@@

The first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
A second level involves providing raw data and code as binary files (PDF or other non-text files) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a pay-wall.
The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following the download of data and code.
The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
In the next section we present standards and tools that can be used to ensure reproducibility.

@@

### Data

@@

### Sharing your research

@@

>>>>

    -   2 - Uses proprietary software that most individuals can afford (*e.g.*, Excel, Matlab (\$500))

@@

    -   1 - Uses expensive proprietary software that only institutions would typically purchase (*e.g.*, ArcGIS standard is \$7000US)

@@

The fourth level includes packaging the analysis as a software package, *e.g.* R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al. [@Khaliq2020] have done. Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conida dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a]. When this level is employed, tools such as Binder,<https://mybinder.org> can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al. used [-@Miorini2018, -@Miorini2019].

-   Example from Grünwald lab/Zhian:

    -   paper <http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI>
    -   github repo <https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests>/<https://github.com/zkamvar/Sudden_Oak_Death_in_Oregon_Forests>

@@

The first level of reproducibility involves openly available research materials such as isolates or strains and/or nucleic acid sequences in public collections and citations for methods used.
A second level involves providing raw data and code as binary files (PDF or other non-text files) in supplemental materials, which do not allow prompt access to the data and running the code because of use of expensive commercial software or a paywall.
The highest level includes efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open source code which are deposited in public repositories and can be run by anyone following the download of data and code.
The first level, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
In the next section we present standards and tools that can be used to ensure reproducibility.

@@

@@

@@

***Need a good closing statement here.***
